---
name: Paul
surname: Johnson
position: "Data Scientist with Experience in Healthcare, Sports Analytics, and Social Science"
phone: "+44 7869 760 968"
www: paulrjohnson.net
email: "paul@paulrjohnson.net"
twitter: paul_johnson89
github: paulj1989
linkedin: paulj1989
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: 
  vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Professional Summary

I am a data scientist based in London, currently working for the NHS South, Central and West CSU in Population Health Management. I am interested in using causal inference and machine learning to help create actionable insights and shape business decisions.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Political Science MA", "2017 - 2020", "University of Houston", "Houston, TX",
  "Global Politics MSc", "2011 - 2012", "University of Southampton", "Southampton, UK",
  "Politics BA Hons", "2008 - 2011", "University of Sussex", "Brighton, UK"
) |> 
  detailed_entries(Degree, Year, Institution, Where)
```

# Work Experience

```{r}
tribble(
  ~ Title, ~ Year, ~ Employer, ~ Where, ~ Details,
  "Principal Data Scientist", "2021 - Present", "NHS South, Central & West", "Remote", 
  "Providing technical expertise in analytics and research-focused projects across the organization, including experimental and observational analysis of healthcare interventions", 
  NA, NA, NA, NA,
  "Building and deploying machine learning models that forecast the daily event counts in A&E and other Urgent and Emergency Care Services",
  NA, NA, NA, NA,
  "Leading the development of organisational expertise in data science, including demonstrating and training colleagues in statistics, machine learning, and programming",
  NA, NA, NA, NA,
  "Supporting the development of the organisation’s infrastructure for developing and deploying data science.",
  
  "Associate BI Consultant", "2021", "NHS South, Central & West", "Remote", 
  "Led research on the wider determinants of health inequalities and the role of deprivation in health outcomes", 
  NA, NA, NA, NA,
  "Supported the Population Health Management team with research design, statistical modeling, and communication and visualization of findings",
  NA, NA, NA, NA,
  "Leading the development of organisational expertise in data science, including demonstrating and training colleagues in statistics, machine learning, and programming",
  NA, NA, NA, NA,
  "Supporting the development of the organisation’s infrastructure for developing and deploying data science",
  
  "Graduate Research Assistant", "2018 - 2020", "University of Houston", "Houston, TX", 
  "Built natural language processing models for research into political language in legal texts", 
  NA, NA, NA, NA,
  "Supported the Population Health Management team with research design, statistical modeling, and communication and visualization of findings",
  NA, NA, NA, NA,
  "Supported the Political Party Database Project in the administering of the expert survey and maintenance of the project website",
  
    "Graduate Teaching Assistant", "2017 - 2019", "University of Houston", "Houston, TX", 
  "Courses: Intro to Comparative Politics, Mexican Politics, Comparative Elections, Media & Politics",
  
  "Fundraising Manager: Product Innovation", "2016 - 2017", "Marie Curie", "London, UK", 
  "Managed Marie Curie’s biggest regular fundraising campaign (Fundraising My Way)", 
  NA, NA, NA, NA,
  "Assisted the development of new fundraising products and the innovation of existing campaigns",

  "Events & Corporate Fundraiser", "2015 - 2016", "World Child Cancer", "London, UK", 
  "Developed, recruited, and managed the charity’s largest charity event to-date (Kilimanjaro trek) and various major events (Ride 100, Great North Run)", 
  NA, NA, NA, NA,
  "Supported the Head of Corporate Fundraising in the successful corporate partnership with Deutsche Bank",
  
) |> 
  tidyr::fill(-Details) |>
  detailed_entries(Employer, Year, Title, Where, Details)
```

# Further Work Experience

```{r}
tribble(
  ~ Title, ~ Year, ~ Employer, ~ Where,
  "Events Coordinator", "2014 - 2015", "Family for Every Child", "London, UK",
  "Oncology Outpatient Clerk", "2013 - 2014", "University Hospital Southampton", "Southampton, UK",
  "Income Management Assistant", "2012 - 2013", "University Hospital Southampton", "Southampton, UK",
) |>
  detailed_entries(Employer, Year, Title, Where)
```

# Skills

## Analytics

Statistics (Frequentist & Bayesian), Data Visualisation, Causal Inference, Machine Learning, Forecasting

## Programming

Python, R, SQL

## Packages

tidyverse, tidymodels, fable, lme4, brms, rstanarm, Shiny, pandas, sklearn, Optuna, spaCy, keras

## Tools

Git, Docker, Quarto, GitHub Actions, DVC, RStudio Workbench & Connect

# Publications & Selected Research

```{r}
tribble(
  ~ Title, ~ Year, ~ Employer, ~ Where, ~ Details,
  "The Nationalization of Mexican Parties", "2020", "P Johnson & F Cantu", "Politica y Gobierno 27 (2)",
  "Measuring the static and dynamic nationalization of Mexican parties, and the importance of national, state, and district factors in explaining the variance of the parties’ electoral support.",
    "Hypothesis Testing for Reliability Statistics: A Permutation Approach", NA, "P Johnson & J Kirkland", NA,
  "Using a series of Monte Carlo studies to demonstrate how researchers can leverage permutation approaches to hypothesis testing for evaluating the statistical reliability of a latent scale.",
) |>
  detailed_entries(Employer, Year, Title, Where, Details)
```

# References

- Available on Request